Face Attractiveness and the Sense of Reality

### 2024-09-02 analysis.Rmd
Update analysis.Rmd

>>>>

```{r message=FALSE, warning=FALSE}
# plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))
df |>
  mutate(Stimulus = fct_relevel(Stimulus, df |>
    group_by(Stimulus) |>
    summarize(Belief_Answer = mean(Belief_Answer)) |>
    ungroup() |>
    arrange(Belief_Answer) |>
    pull(Stimulus) |>
    as.character())) |>
  # mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |>
  ggplot(aes(x = Belief_Answer, y = Stimulus, fill = Stimulus)) +
  ggdist::stat_slab(scale = 4, slab_alpha = 2/3, normalize = "groups", color = "black", size = 0.2) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(0.02, 0)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0, 0),
    breaks = c(-0.95, 0, 0.95),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "grey", color = "white") +
  ggside::scale_xsidey_continuous(expand = c(0, 0))
```
